---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gitdown

<!-- badges: start -->
<!-- badges: end -->

The goal of {gitdown} is to build a bookdown report of commit messages arranged according to a pattern. Book can be organised according to git tags, issues mentionned (*e.g.* `#123`) or any custom character chain included in your git commit messages (*e.g.* `category_` for use like `category_ui`, `category_doc`, ...).

## Installation

You can install the last version of {gitdown} from Github:

``` r
remotes::install_github("gitdown")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(dplyr)
library(gitdown)
## Create fake repository for the example
repo <- fake_repo()
```

Get commits with issues mentionned. The searched pattern is a `#` followed by at least one number: `pattern = "#[[:digit:]]+"`.

```{r}
get_commits_pattern(repo, pattern = "#[[:digit:]]+", ref = "master") %>% 
  select(pattern, everything())
```

